### 2023-03-06 article3.qmd
update

```{r, load libraries}
library(akima)
library(broom)
library(tidyverse)
library(cmocean)
library(lubridate)
library(scales)
library(patchwork)
library(viridis)
library(ggridges)
library(ggvis)
library(pracma)
library(gbm)
library(MLmetrics)
library(purrr)
library(arrow)
library(plotly)
library(oce)
library(ggplot2)
library(latex2exp)
library(cowplot)
library(RColorBrewer)
library(vroom)
library(castr)
library(reactablefmtr)
library(gt)
library(gtExtras)
library(spatialrisk)
```

@@

# add levels for some field
all_floats <- all_floats |> mutate(wmo = factor(wmo, levels = c(6904240,4903634,6904241,1902578)),
                                   park_depth = factor(park_depth, levels = c('200 m', '500 m', '1000 m')))

# summarize localization of floats
argo_map <- all_floats |> select(WMO = wmo, cycle, lat, lon) |> drop_na(lat) |> dplyr::group_by(WMO, cycle) |> mutate(WMO = factor(WMO)) |>
  dplyr::summarise(lat = mean(lat), lon = mean(lon))

@@

# map positions of floats
world_data <- map_data("world")
w <- list(geom_polygon(aes(long, lat, group=group), data=world_data, fill="grey70"), coord_quickmap())

ggplot(argo_map) + w + geom_path(aes(lon, lat, colour = WMO), size = 1) +
  geom_point(aes(lon, lat, colour = WMO), size = 1.5) +
  scale_color_brewer(palette = 'Dark2') +
  theme_bw() +
  #scale_colour_manual(values = c('#a6cee3', '#33a02c', '#b2df8a', '#1f78b4')) +
  coord_cartesian(xlim = c(-55, -40), ylim = c(55,65)) + geom_point(data = argo_map_first, aes(lon, lat), shape = 17, size = 3) +
  geom_point(data = argo_map_last, aes(lon, lat, colour = WMO), size = 3) +
  geom_point(data = argo_map_last, aes(lon, lat, fill = WMO), size = 3, shape = 1) +
  labs(x = 'longitude', y = 'latitude') +
  #https://aosmith.rbind.io/2020/07/09/ggplot2-override-aes/#suppress-aesthetics-from-part-of-the-legend
  guides(color = guide_legend(override.aes = list(size = c(1.5,1.5,1.5,1.5),
                                                  shape = c(NA, NA, NA, NA))))

@@

In order to compute $F_{small}$, we firstly computed the slope of each group of observations between jumps (positive and negative, see @fig-estapa-method_article). Undefined slopes (a single point between two jumps) were removed as well as any negative slope assuming that either the so-called fit failed (leading to undetected jumps) either the transmissometer window was perturbed by something else than the pump cleaning the optical window. Afterwards, we computed the weighted average slope ($slope_{w}$) using the previously computed slopes of each remaining group in order to derive the small particles flux using the relationship of @Estapa2022

@@

@@

# remove negative jump, if any
check_colour <- unique(tmp3$colour)
if(length(check_colour) == 3){
  index_neg_jump <- which(tmp3$colour == 'negative jump')
  tmp3 <- tmp3[-c(index_neg_jump, index_neg_jump+1),]
  tmp3 <- tmp3 |> mutate(diff_jump = cp - lag(cp))
  even_indexes <- seq(2,nrow(tmp3),2)
  tmp3 <- tmp3[even_indexes,]
}else if(length(check_colour) == 2){
  tmp3 <- tmp3 |> mutate(diff_jump = cp - lag(cp))
  even_indexes <- seq(2,nrow(tmp3),2)
  tmp3 <- tmp3[even_indexes,]
}else{ # NO jump
  tmp3 <- NULL
  }

@@

  # compute a Z score (assuming a normal distribution of the slopes) on the slopes
  tmp <- tmp |> mutate(zscore = (slope - mean(slope, na.rm = T))/sd(slope, na.rm = T))

@@

  # remove negative jumps, if any
  check_colour <- unique(tmp2$colour)
  # if(length(check_colour) == 3){ # there is at least a negative jump
  #   index_neg_jump <- which(tmp2$colour == 'negative jump')
  #   tmp2 <- tmp2[-c(index_neg_jump, index_neg_jump+1),]
  #   tmp2 <- tmp2 |> mutate(diff_jump = cp - lag(cp)) 
  #   even_indexes <- seq(2,nrow(tmp2),2)
  #   tmp2 <- tmp2[even_indexes,]
  # }else if(length(check_colour) == 2){ # only positive jumps
  #   tmp2 <- tmp2 |> mutate(diff_jump = cp - lag(cp)) 
  #   even_indexes <- seq(2,nrow(tmp2),2)
  #   tmp2 <- tmp2[even_indexes,]
  # }else{ # No jump
  #   tmp2 <- NULL
  # }
  if(length(check_colour) >= 2){ # there is a least a jump (positive or negative)
    tmp2 <- tmp2 |> mutate(diff_jump = cp - lag(cp)) 
    even_indexes <- seq(2,nrow(tmp2),2)
    tmp2 <- tmp2[even_indexes,]
  }else{ # No jump
    tmp2 <- NULL
  }

@@

  # to plot subgroups
  part_slope_tmp <- part_slope |> mutate(dates = time, colour = 'slope')

@@

  return(df)

}
```

@@

# remove bad data from float 6904241
float_6904241_slope <- float_6904241 |> filter(cycle < 20)
# create dataframe for all drifting data (for all floats)
all_floats_slope <- rbind(float_4903634, float_6904240, float_6904241_slope, float_1902578)
all_floats_slope <- all_floats_slope |> filter(PhaseName == 'PAR') |> drop_na(cp) |> select(depth = pres, cp, dates = juld, park_depth, wmo, cycle) |>
   mutate(wmo = factor(wmo, levels = c(6904240,4903634,6904241,1902578)),
          park_depth = factor(park_depth, levels = c('200 m', '500 m', '1000 m')))

@@

# keep the good fluxes
cflux <- res |> mutate(drifting_time = difftime(max_time, min_time, units = 'days'), WMO = factor(wmo))

@@

uvp_data <- all_floats |> filter(PhaseName == 'PAR') |> mutate(month = month(juld), week = week(juld), DOY = yday(juld), short_date = ymd(juld)) |> select(juld, month, week, DOY, short_date, cycle, wmo, park_depth, all_of(lpm_class)) |> 
  drop_na(NP_Size_102) |> mutate(juld = as_date(juld), WMO = factor(wmo))

uvp_data <- uvp_data |> pivot_longer(cols = lpm_class, names_to = 'size', values_to = 'conc') |> mutate(size = size |> str_remove('NP_Size_') |> as.numeric())

# compute daily mean chla for each float at each cycle and at each drifting depth
mean_uvp_data <- uvp_data |> group_by(cycle, WMO, size, park_depth, juld) |> summarize(mean_conc = mean(conc, na.rm=T))
```

@@

test <- tmp200m$data[[2]] |> filter(is.finite(y)) |> group_by(PANEL) |> summarize(index_max = which.max(y), max_date = x[index_max]) |> mutate(date_max = as_date(max_date, origin = "1970-01-01"))
test$size <- unique(uvp_data$size)

@@

test <- tmp500m$data[[2]] |> filter(is.finite(y)) |> group_by(PANEL) |> summarize(index_max = which.max(y), max_date = x[index_max]) |> mutate(date_max = as_date(max_date, origin = "1970-01-01"))
test$size <- unique(uvp_data$size)

@@

test <- tmp1000m$data[[2]] |> filter(is.finite(y)) |> group_by(PANEL) |> summarize(index_max = which.max(y), max_date = x[index_max]) |> mutate(date_max = as_date(max_date, origin = "1970-01-01"))
test$size <- unique(uvp_data$size)

@@

parking_data <- rbind(float_4903634, float_6904240, float_6904241_slope, float_1902578)
parking_data <- parking_data |> filter(PhaseName == 'PAR') |> drop_na(NP_Size_102) |> select(park_depth, all_of(lpm_class), dates = juld, park_depth, wmo, cycle) |> mutate(wmo = factor(wmo, levels = c(6904240,4903634,6904241,1902578)),
                                   park_depth = factor(park_depth, levels = c('200 m', '500 m', '1000 m')))
parking_spectra <- parking_data |> dplyr::select(NP_Size_256:NP_Size_1290)

parking_data <- parking_data |> mutate(guidi_flux = compute_flux(12.5, 3.81, parking_spectra)) #|> group_by(park_depth, cycle, wmo)

@@

parking_spectra_rainer <- parking_data |> dplyr::select(lpm_class)
parking_data <- parking_data |> mutate(rainer_flux = compute_flux_rainer(2.8649, 2.24, parking_spectra_rainer)) 
parking_data <- parking_data |> mutate(iversen_flux = compute_flux(273, 4.27, parking_spectra))

# plot it
comparison_flux_ost_uvp <- merge(parking_data, cflux) |> mutate(total_flux = small_flux + big_flux)

# https://stackoverflow.com/questions/41077199/how-to-use-r-ggplot-stat-summary-to-plot-median-and-quartiles
ggplot(comparison_flux_ost_uvp) + geom_line(aes(x = date, y = total_flux)) + facet_wrap(~wmo~park_depth, scales = 'free_y', nrow = 4) +
  geom_errorbar(aes(x = date, y = guidi_flux),
                      stat = 'summary',
                      fun.min = function(z) {quantile(z, 0.25)},
                      fun.max = function(z) {quantile(z, 0.75)},
                      fun = median, colour = 'red', width = 5) +
  geom_line(aes(x = date, y = guidi_flux),
                      stat = 'summary',
                      fun = median, colour = 'red') + scale_y_continuous(trans = 'log10') + theme_bw()

@@

```{r, correlations between OST and UVP carbon fluxes}
#| label: tbl-correlation
#| tbl-cap: TODO
correlations <- comparison_flux_ost_uvp |> select(park_depth, wmo, cycle, guidi_flux, small_flux, big_flux, date, total_flux) |> group_by(wmo, park_depth, cycle) |> mutate(median_guidi_flux = median(guidi_flux)) |> group_by(park_depth, wmo) |> summarise(cor_small = round(cor(median_guidi_flux, small_flux),2), cor_big = round(cor(median_guidi_flux, big_flux),2), cor_total = round(cor(median_guidi_flux, total_flux),2))

@@

@@

  # remove negative jumps, if any
  check_colour <- unique(tmp2$colour)
  if(length(check_colour) >= 2){ # there is a least a jump (positive or negative)
    tmp2 <- tmp2 |> mutate(diff_jump = cp - lag(cp)) 
    even_indexes <- seq(2,nrow(tmp2),2)
    tmp2 <- tmp2[even_indexes,]
  }else{ # No jump
    tmp2 <- NULL
  }

@@

  # clean data to send
  slope_df <- slope_df |> arrange(min_time) |> mutate(min_drifting_time = df$min_time, max_drifting_time = df$max_time, small_flux = df$small_flux, big_flux = df$big_flux, park_depth = data$park_depth[1], wmo = data$wmo[1],cycle = data$cycle[1])
  if(is.null(tmp3)){
    big_jump <- tmp3
  }else{
     big_jump <- tmp3 |> mutate(park_depth = data$park_depth[1], wmo = data$wmo[1],cycle = data$cycle[1]) 
  }

@@

uvp_drifting <- all_floats |> filter(PhaseName == 'PAR') |> select(juld, cycle, wmo, park_depth, all_of(lpm_class)) |> 
  drop_na(NP_Size_102) |> mutate(date = as_date(juld))

@@

# compute biovolume and add them to the dataframe
spectra_biovolume <- tibble(as.data.frame(t(t(uvp_drifting[,all_of(lpm_class)])*biovolumes)))
colnames(spectra_biovolume) <- colnames(spectra_biovolume)|> str_replace('NP_Size', 'Biovolume')
biovolumes_names <- colnames(spectra_biovolume)
uvp_drifting <- cbind(uvp_drifting, spectra_biovolume) |> rowwise() |> mutate(total_biovolume = sum(across(all_of(biovolumes_names))))

@@

test <- data.frame()
for (i in wmo){
  max_cycle <- as.numeric(all_floats_slope |> filter(wmo == i) |> dplyr::summarise(max_cycle = max(cycle)))
  for (j in park_depth){
    for (k in seq(1:max_cycle)){
      tmp_uvp <- filter(uvp_drifting, wmo == i, cycle == k, park_depth == j) |> arrange(juld) |> select(juld, cycle, wmo, park_depth, total_biovolume) #, biovolumes_names)
      tmp_ost <- res_slope |> filter(wmo == i, cycle == k, park_depth == j)
      tmp <- assign_time_group(tmp_uvp, tmp_ost)
      #tmp2 <- tmp |> filter(!is.na(group)) |> group_by(group) |> mutate(uvp_points = n(), min_date = min(juld), max_date = max(juld), mean_date = mean(floor_date(juld))) # https://stackoverflow.com/questions/44814435/calculate-average-daily-value-from-large-data-set-with-r-standard-format-date-ti
      tmp2 <- tmp |> filter(!is.na(group)) |> group_by(group) |> mutate(uvp_points = n(), mean_date = mean(floor_date(juld))) 
      tmp3 <- merge(tmp2, tmp_ost) |> group_by(group, cycle, wmo, park_depth) |> summarize(mean_date = unique(mean_date), uvp_points = unique(uvp_points), ost_points = unique(nb_points), group_total_biovolume = sum(total_biovolume), slope = unique(slope), weighted_group_biovolume = group_total_biovolume/uvp_points)
      test <- rbind(test, tmp3)
    }
  }
}

ggplot(test) + geom_line(aes(x = mean_date, y = weighted_group_biovolume)) + facet_wrap(~wmo~park_depth, scales = 'free_y', nrow = 4) +
ggplot(test) + geom_line(aes(x = mean_date, y = slope)) + facet_wrap(~wmo~park_depth, scales = 'free_y', nrow = 4)

# check
test2 <- test |> group_by(wmo, cycle) |> mutate(mean_mean_date = mean(floor_date(mean_date)))

ggplot(test2) +
  geom_pointrange(aes(x = mean_mean_date, y = weighted_group_biovolume),
                      stat = 'summary',
                      fun.min = function(z) {quantile(z, 0.25)},
                      fun.max = function(z) {quantile(z, 0.75)},
                      fun = median, colour = 'black', size = .1) +
    facet_wrap(~wmo~park_depth, scales = 'free_y', nrow = 4) +

ggplot(test2) +
  geom_pointrange(aes(x = mean_mean_date, y = slope),
                      stat = 'summary',
                      fun.min = function(z) {quantile(z, 0.25)},
                      fun.max = function(z) {quantile(z, 0.75)},
                      fun = median, colour = 'black', size = .1) +
    facet_wrap(~wmo~park_depth, scales = 'free_y', nrow = 4)

test2 |> group_by(wmo, park_depth) |> summarize(correl = cor(slope, weighted_group_biovolume))

ggplot(test) + geom_point(aes(x = log(slope), y = log(weighted_group_biovolume))) + facet_wrap(~park_depth)
#ggplot(test) + geom_point(aes(x = slope, y = weighted_group_biovolume)) + facet_wrap(~park_depth)

# what about jump values with uvp measurements at jump
uvp_drifting <- uvp_drifting |> mutate(num_date = as.numeric(juld))
res_jumps <- res_jumps |> mutate(num_date = as.numeric(dates))

@@

# add couple info
d_chla <- d_chla |> mutate(group = if_else(wmo %in% c(6904240,4903634), '6904240 - 4903634', '6904241 - 1902578'))

@@

@@

```{r, test gt table}

>>>>

```{r, load libraries}
library(tidyverse)
library(akima)
library(broom)
library(cmocean)
library(lubridate)
library(scales)
library(patchwork)
library(viridis)
library(ggridges)
library(ggvis)
library(pracma)
library(gbm)
library(MLmetrics)
library(purrr)
library(arrow)
library(plotly)
library(oce)
library(ggplot2)
library(latex2exp)
library(cowplot)
library(RColorBrewer)
library(vroom)
library(castr)
library(reactablefmtr)
library(gt)
#library(gtExtras)
library(spatialrisk)
library(ggOceanMaps)
```

@@

# add levels for some field
all_floats <- all_floats |> dplyr::mutate(wmo = factor(wmo, levels = c(6904240,4903634,6904241,1902578)),
                                   park_depth = factor(park_depth, levels = c('200 m', '500 m', '1000 m')))

# summarize localization of floats
argo_map <- all_floats |> select(WMO = wmo, cycle, lat, lon) |> drop_na(lat) |> dplyr::group_by(WMO, cycle) |> dplyr::mutate(WMO = factor(WMO)) |>
  dplyr::summarise(lat = mean(lat), lon = mean(lon))

@@

# # map positions of floats
# world_data <- map_data("world")
# w <- list(geom_polygon(aes(long, lat, group=group), data=world_data, fill="grey70"), coord_quickmap())
# 
# ggplot(argo_map) + w + geom_path(aes(lon, lat, colour = WMO), size = 1) +
#   geom_point(aes(lon, lat, colour = WMO), size = 1.5) +
#   scale_color_brewer(palette = 'Dark2') +
#   theme_bw() +
#   #scale_colour_manual(values = c('#a6cee3', '#33a02c', '#b2df8a', '#1f78b4')) +
#   coord_cartesian(xlim = c(-55, -40), ylim = c(55,65)) + geom_point(data = argo_map_first, aes(lon, lat), shape = 17, size = 3) +
#   geom_point(data = argo_map_last, aes(lon, lat, colour = WMO), size = 3) +
#   geom_point(data = argo_map_last, aes(lon, lat, fill = WMO), size = 3, shape = 1) +
#   labs(x = 'longitude', y = 'latitude') +
#   #https://aosmith.rbind.io/2020/07/09/ggplot2-override-aes/#suppress-aesthetics-from-part-of-the-legend
#   guides(color = guide_legend(override.aes = list(size = c(1.5,1.5,1.5,1.5),
#                                                   shape = c(NA, NA, NA, NA))))

# prepare data for geomapping, see https://mikkovihtakari.github.io/ggOceanMaps/
argo_map_geo <- transform_coord(argo_map) |> dplyr::mutate(cycle = argo_map$cycle, WMO = as.factor(argo_map$WMO))
argo_map_last_geo <- transform_coord(argo_map_last) |> mutate(WMO = as.factor(argo_map_last$WMO))

basemap(limits = c(-55,-40,55,65), bathymetry = T) +
  geom_path(data = argo_map_geo, aes(lon, lat, colour = WMO), size = 1.5) + 
  geom_point(data = argo_map_geo, aes(x= lon, y = lat, colour = WMO), size = 3) +
  scale_color_brewer(palette = 'Dark2') + theme_bw() +
  geom_point(data = transform_coord(argo_map_first), aes(lon, lat), shape = 17, size = 3) +
  geom_point(data = argo_map_last_geo, aes(lon, lat, colour = WMO), size = 6) +
  geom_point(data = argo_map_last_geo, aes(lon, lat), fill = 'black', size = 6, shape = 1) +
  #https://aosmith.rbind.io/2020/07/09/ggplot2-override-aes/#suppress-aesthetics-from-part-of-the-legend
  guides(color = guide_legend(override.aes = list(size = c(1.5,1.5,1.5,1.5),
                                                  shape = c(NA, NA, NA, NA))))

@@

In order to compute $F_{small}$, we firstly computed the slope of each group of observations between jumps (positive and negative, see @fig-estapa-method_article). Undefined slopes (a single point between two jumps) were removed as well as any negative slope assuming that either the so-called fit failed (leading to undetected jumps) either the transmissometer window was perturbed by something else than the pump cleaning the optical window. Afterwards, we computed the weighted average slope ($slope_{w}$) using the previously computed slopes of each remaining group in order to derive the small particles flux using the linear relationship between the beam attenuance flux and the POC flux (see first panel of Figure 2 in @Estapa2023-oz).

@@

  data <- data |> arrange(dates)

@@

# remove negative jump, if any
check_colour <- unique(tmp3$colour)
if(length(check_colour) == 3){
  index_neg_jump <- which(tmp3$colour == 'negative jump')
  tmp3 <- tmp3[-c(index_neg_jump, index_neg_jump+1),]
  tmp3 <- tmp3 |> dplyr::mutate(diff_jump = cp - lag(cp))
  even_indexes <- seq(2,nrow(tmp3),2)
  tmp3 <- tmp3[even_indexes,]
}else if(length(check_colour) == 2){
  tmp3 <- tmp3 |> dplyr::mutate(diff_jump = cp - lag(cp))
  even_indexes <- seq(2,nrow(tmp3),2)
  tmp3 <- tmp3[even_indexes,]
}else{ # NO jump
  tmp3 <- NULL
  }

@@

  # compute a Z score (assuming a normal distribution of the slopes) on the slopes
  tmp <- tmp |> dplyr::mutate(zscore = (slope - mean(slope, na.rm = T))/sd(slope, na.rm = T))

@@

  # remove negative jumps, if any
  check_colour <- unique(tmp2$colour)
  # if(length(check_colour) == 3){ # there is at least a negative jump
  #   index_neg_jump <- which(tmp2$colour == 'negative jump')
  #   tmp2 <- tmp2[-c(index_neg_jump, index_neg_jump+1),]
  #   tmp2 <- tmp2 |> dplyr::mutate(diff_jump = cp - lag(cp)) 
  #   even_indexes <- seq(2,nrow(tmp2),2)
  #   tmp2 <- tmp2[even_indexes,]
  # }else if(length(check_colour) == 2){ # only positive jumps
  #   tmp2 <- tmp2 |> dplyr::mutate(diff_jump = cp - lag(cp)) 
  #   even_indexes <- seq(2,nrow(tmp2),2)
  #   tmp2 <- tmp2[even_indexes,]
  # }else{ # No jump
  #   tmp2 <- NULL
  # }
  if(length(check_colour) >= 2){ # there is a least a jump (positive or negative)
    tmp2 <- tmp2 |> dplyr::mutate(diff_jump = cp - lag(cp)) 
    even_indexes <- seq(2,nrow(tmp2),2)
    tmp2 <- tmp2[even_indexes,]
  }else{ # No jump
    tmp2 <- NULL
  }

@@

  # to plot subgroups
  part_slope_tmp <- part_slope |> dplyr::mutate(dates = time, colour = 'slope')

@@

  return(df)
  #return(jump_plot)

# tmp <- all_floats_slope |> filter(wmo == 6904240, park_depth == '1000 m', cycle == 21)
# plot_jumps(tmp)
```

@@

# remove bad data from float 6904241
float_6904241_slope <- float_6904241 |> filter(cycle < 20)
# create dataframe for all drifting data (for all floats)
all_floats_slope <- rbind(float_4903634, float_6904240, float_6904241_slope, float_1902578)
all_floats_slope <- all_floats_slope |> filter(PhaseName == 'PAR') |> drop_na(cp) |> select(depth = pres, cp, dates = juld, park_depth, wmo, cycle) |>
   dplyr::mutate(wmo = factor(wmo, levels = c(6904240,4903634,6904241,1902578)),
          park_depth = factor(park_depth, levels = c('200 m', '500 m', '1000 m')))

@@

# keep the good fluxes
cflux <- res |> dplyr::mutate(drifting_time = difftime(max_time, min_time, units = 'days'), WMO = factor(wmo))

@@

uvp_data <- all_floats |> filter(PhaseName == 'PAR') |> dplyr::mutate(month = month(juld), week = week(juld), DOY = yday(juld), short_date = ymd(juld)) |> select(juld, month, week, DOY, short_date, cycle, wmo, park_depth, all_of(lpm_class)) |> 
  drop_na(NP_Size_102) |> dplyr::mutate(juld = as_date(juld), WMO = factor(wmo))

uvp_data <- uvp_data |> pivot_longer(cols = lpm_class, names_to = 'size', values_to = 'conc') |> dplyr::mutate(size = size |> str_remove('NP_Size_') |> as.numeric())

# compute daily mean chla for each float at each cycle and at each drifting depth
mean_uvp_data <- uvp_data |> dplyr::group_by(cycle, WMO, size, park_depth, juld) |> dplyr::summarize(mean_conc = mean(conc, na.rm=T))
```

@@

test <- tmp200m$data[[2]] |> filter(is.finite(y)) |> group_by(PANEL) |> dplyr::summarize(index_max = which.max(y), max_date = x[index_max]) |> dplyr::mutate(date_max = as_date(max_date, origin = "1970-01-01"))
test$size <- unique(uvp_data$size)

@@

test <- tmp500m$data[[2]] |> filter(is.finite(y)) |> group_by(PANEL) |> dplyr::summarize(index_max = which.max(y), max_date = x[index_max]) |> dplyr::mutate(date_max = as_date(max_date, origin = "1970-01-01"))
test$size <- unique(uvp_data$size)

@@

test <- tmp1000m$data[[2]] |> filter(is.finite(y)) |> group_by(PANEL) |> dplyr::summarize(index_max = which.max(y), max_date = x[index_max]) |> dplyr::mutate(date_max = as_date(max_date, origin = "1970-01-01"))
test$size <- unique(uvp_data$size)

@@

parking_data <- rbind(float_4903634, float_6904240, float_6904241_slope, float_1902578)
parking_data <- parking_data |> filter(PhaseName == 'PAR') |> drop_na(NP_Size_102) |> select(park_depth, all_of(lpm_class), dates = juld, park_depth, wmo, cycle) |> dplyr::mutate(wmo = factor(wmo, levels = c(6904240,4903634,6904241,1902578)),
                                   park_depth = factor(park_depth, levels = c('200 m', '500 m', '1000 m')))
parking_spectra <- parking_data |> dplyr::select(NP_Size_256:NP_Size_1290)

parking_data <- parking_data |> dplyr::mutate(guidi_flux = compute_flux(12.5, 3.81, parking_spectra)) #|> group_by(park_depth, cycle, wmo)

@@

parking_spectra_rainer <- parking_data |> dplyr::select(lpm_class)
parking_data <- parking_data |> dplyr::mutate(rainer_flux = compute_flux_rainer(2.8649, 2.24, parking_spectra_rainer)) 
parking_data <- parking_data |> dplyr::mutate(iversen_flux = compute_flux(273, 4.27, parking_spectra))

# plot it
comparison_flux_ost_uvp <- merge(parking_data, cflux) |> dplyr::mutate(total_flux = small_flux + big_flux)

# add guidi flux obtained with fminsearch
# mean_d <- c(0.29042685, 0.36591491, 0.46102389, 0.58085371, 0.73182981, 0.92204779, 1.16170742, 1.46365963)
# comparison_flux_ost_uvp <-  comparison_flux_ost_uvp[-c(bad_index),]
# ost_flux <- comparison_flux_ost_uvp$total_flux
# spectra <- comparison_flux_ost_uvp |> select(NP_Size_256:NP_Size_1290)
# # some spectra gives 0 for all classes - makes a buggy fminsearch -> remove those lines
# bad_index <- which((rowSums(t(t(spectra)))) == 0)
# spectra <- spectra[-c(bad_index),]
# compute_flux <- function(x) sum((log10(rowSums(t(t(spectra)*x[1]*mean_d ** x[2]))) - log10(ost_flux))**2)
# x0 <- c(12.5, 2.2)
# fminsearch(compute_flux, x0 = x0)
# fmincon(x0 = x0, compute_flux, lb = c(1, 1.5), ub = c(1000, 3))

# add guidi flux using fminsearch using the optimize function of scipy in python (see a paper of someoe who did it, see Giering 2020 ou willimaoson et giering 2022)
comparison_flux_ost_uvp <- comparison_flux_ost_uvp |> dplyr::mutate(guidi_flux_fminsearch = compute_flux(21.98, 1.18, parking_spectra))

# https://stackoverflow.com/questions/41077199/how-to-use-r-ggplot-stat-summary-to-plot-median-and-quartiles
ggplot(comparison_flux_ost_uvp) + geom_line(aes(x = date, y = total_flux)) + facet_wrap(~wmo~park_depth, scales = 'free_y', nrow = 4) +
  geom_errorbar(aes(x = date, y = guidi_flux),
                      stat = 'summary',
                      fun.min = function(z) {quantile(z, 0.25)},
                      fun.max = function(z) {quantile(z, 0.75)},
                      fun = median, colour = '#E31B23', width = 5) +
    geom_line(aes(x = date, y = guidi_flux),
                      stat = 'summary',
                      fun = median, colour = '#E31B23') +
    geom_errorbar(aes(x = date, y = iversen_flux),
                      stat = 'summary',
                      fun.min = function(z) {quantile(z, 0.25)},
                      fun.max = function(z) {quantile(z, 0.75)},
                      fun = median, colour = '#003366', width = 5) +
    geom_line(aes(x = date, y = iversen_flux),
                      stat = 'summary',
                      fun = median, colour = '#003366') + 
  scale_y_continuous(trans = 'log10') + theme_bw() + labs(x = 'Month', y = TeX('$F_{total}$ (mg C m$^{-2}$ day$^{-1}$)'))

@@

ici je compare finalement un système ultra productif (iversen) et un système pas produtif (lionel) -> on se situerait entre les deux. Après je peux fournir els valeurs que j'ai trouvées avec le fminsearch avec la fonctiono optimize depython (21.98 et 1.18. Mais bon, cela assumerait que 'lon pourrait prendre l'OST comme référence, ce qui est un peu too much..)

```{r, correlations between OST and UVP carbon fluxes}
#| label: tbl-correlation
#| tbl-cap: TODO
correlations <- comparison_flux_ost_uvp |> dplyr::select(park_depth, wmo, cycle, guidi_flux, small_flux, big_flux, date, total_flux) |> dplyr::group_by(wmo, park_depth, cycle) |> dplyr::mutate(median_guidi_flux = median(guidi_flux)) |> dplyr::group_by(park_depth, wmo) |> dplyr::summarize(cor_small = round(cor(median_guidi_flux, small_flux),2), cor_big = round(cor(median_guidi_flux, big_flux),2), cor_total = round(cor(median_guidi_flux, total_flux),2))

@@

  # build dataframe to plot each subgroup
  part1 <- slope_df |> dplyr::select(group, time = min_time, cp = first_cp)
  part2 <- slope_df |> select(group, time = max_time, cp = last_cp)
  part_slope <- rbind(part1, part2)

@@

  # remove negative jumps, if any
  check_colour <- unique(tmp2$colour)
  if(length(check_colour) >= 2){ # there is a least a jump (positive or negative)
    tmp2 <- tmp2 |> dplyr::mutate(diff_jump = cp - lag(cp)) 
    even_indexes <- seq(2,nrow(tmp2),2)
    tmp2 <- tmp2[even_indexes,]
  }else{ # No jump
    tmp2 <- NULL
  }

@@

  # clean data to send
  slope_df <- slope_df |> arrange(min_time) |> dplyr::mutate(min_drifting_time = df$min_time, max_drifting_time = df$max_time, small_flux = df$small_flux, big_flux = df$big_flux, park_depth = data$park_depth[1], wmo = data$wmo[1],cycle = data$cycle[1])
  if(is.null(tmp3)){
    big_jump <- tmp3
  }else{
     big_jump <- tmp3 |> dplyr::mutate(park_depth = data$park_depth[1], wmo = data$wmo[1],cycle = data$cycle[1]) 
  }

@@

uvp_drifting <- all_floats |> filter(PhaseName == 'PAR') |> select(juld, cycle, wmo, park_depth, all_of(lpm_class)) |> 
  drop_na(NP_Size_102) |> dplyr::mutate(date = as_date(juld))

@@

# compute biovolume and add them to the dataframe
spectra_biovolume <- tibble(as.data.frame(t(t(uvp_drifting[,all_of(lpm_class)])*biovolumes)))
colnames(spectra_biovolume) <- colnames(spectra_biovolume)|> str_replace('NP_Size', 'Biovolume')
biovolumes_names <- colnames(spectra_biovolume)
uvp_drifting <- cbind(uvp_drifting, spectra_biovolume) |> rowwise() |> dplyr::mutate(total_biovolume = sum(across(all_of(biovolumes_names))))

@@

# test <- data.frame()
# for (i in wmo){
#   max_cycle <- as.numeric(all_floats_slope |> filter(wmo == i) |> dplyr::summarise(max_cycle = max(cycle)))
#   for (j in park_depth){
#     for (k in seq(1:max_cycle)){
#       tmp_uvp <- filter(uvp_drifting, wmo == i, cycle == k, park_depth == j) |> arrange(juld) |> select(juld, cycle, wmo, park_depth, total_biovolume) 
#       tmp_ost <- res_slope |> filter(wmo == i, cycle == k, park_depth == j)
#       if(nrow(tmp_uvp) == 0 | nrow(tmp_ost) == 0){
#         next
#       }else{
#       tmp <- assign_time_group(tmp_uvp, tmp_ost)
#       #tmp2 <- tmp |> filter(!is.na(group)) |> dplyr::group_by(group) |> dplyr::mutate(uvp_points = n(), min_date = min(juld), max_date = max(juld), mean_date = mean(floor_date(juld))) # https://stackoverflow.com/questions/44814435/calculate-average-daily-value-from-large-data-set-with-r-standard-format-date-ti
#       tmp2 <- tmp |> filter(!is.na(group)) |> group_by(group) |> dplyr::mutate(uvp_points = n(), mean_date = mean(floor_date(juld)))
#       tmp3 <- merge(tmp2, tmp_ost) |> dplyr::group_by(group, cycle, wmo, park_depth) |> dplyr::summarize(mean_date = unique(mean_date), uvp_points = unique(uvp_points), ost_points = unique(nb_points), group_total_biovolume = sum(total_biovolume), slope = unique(slope), weighted_group_biovolume = group_total_biovolume/uvp_points)
#       test <- rbind(test, tmp3)
#       }
#     }
#   }
# }

# write data because it's long
# vroom_write(test, file = '/home/flo/dox/THESIS/DATA/ARGO/slope_vs_biovolume.csv')

# load data computed with the above commented code
slope_vs_biovolume <- vroom::vroom('DATA/ARGO/slope_vs_biovolume.csv')
slope_vs_biovolume <- slope_vs_biovolume |> mutate(park_depth = factor(park_depth, levels = c('200 m', '500 m', '1000 m')))

# ggplot(test) + geom_line(aes(x = mean_date, y = weighted_group_biovolume)) + facet_wrap(~wmo~park_depth, scales = 'free_y', nrow = 4) +
# ggplot(test) + geom_line(aes(x = mean_date, y = slope)) + facet_wrap(~wmo~park_depth, scales = 'free_y', nrow = 4)

# check
# test2 <- test |> group_by(wmo, cycle) |> dplyr::mutate(mean_mean_date = mean(floor_date(mean_date))) 
# 
# ggplot(test2) +
#   geom_pointrange(aes(x = mean_mean_date, y = weighted_group_biovolume),
#                       stat = 'summary',
#                       fun.min = function(z) {quantile(z, 0.25)},
#                       fun.max = function(z) {quantile(z, 0.75)},
#                       fun = median, colour = 'black', size = .1) +
#     facet_wrap(~wmo~park_depth, scales = 'free_y', nrow = 4) +
#   
# ggplot(test2) +
#   geom_pointrange(aes(x = mean_mean_date, y = slope),
#                       stat = 'summary',
#                       fun.min = function(z) {quantile(z, 0.25)},
#                       fun.max = function(z) {quantile(z, 0.75)},
#                       fun = median, colour = 'black', size = .1) +
#     facet_wrap(~wmo~park_depth, scales = 'free_y', nrow = 4) 
# 
# test2 |> group_by(wmo, park_depth) |> summarize(correl = cor(slope, weighted_group_biovolume))

ggplot(slope_vs_biovolume) + geom_point(aes(x = log(slope), y = log(weighted_group_biovolume))) + facet_wrap(~park_depth) + labs(x = 'OST slope [UNITS]', y = 'UVP biovolume [UNITS]') #+ theme(axis.title.x = element_blank())
#ggplot(test) + geom_point(aes(x = slope, y = weighted_group_biovolume)) + facet_wrap(~park_depth)

# what about jump values with uvp measurements at jump
uvp_drifting <- uvp_drifting |> dplyr::mutate(num_date = as.numeric(juld))
res_jumps <- res_jumps |> dplyr::mutate(num_date = as.numeric(dates))

@@

# add couple info
d_chla <- d_chla |> dplyr::mutate(group = if_else(wmo %in% c(6904240,4903634), '6904240 - 4903634', '6904241 - 1902578'))

@@

all_sinking_speed |> ggplot() + geom_point(aes(y = sinking_speed_below_threshold, x = size))

@@
